---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# contouR

<!-- badges: start -->
<!-- badges: end -->

contouR is a package that is a wraparound for `ggplot2::geom_contour()` to use for generative art. `geom_contour()` allows one to visualize 3D surfaces in 2D by using x, y and z coordinates. To change it up from the typical contour plot, there are three different distributions used to generate the z values: `rnorm()`, `runif()`, and `rpois()`.

## Installation

You can install the current verion of contouR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Ijeamakaanyene/contouR")
```

If you make any fun art with this package, please feel free to contact me on twitter <a href="https://twitter.com/ijeamaka_a"> @ijeamaka_a</a> to show it off `r emo::ji("moon")`

## Example: without rings

```{r example, fig.width=6, fig.height = 6}
library(contouR)

#set up your data
setup = contour_grid(grid_size = 30, point_dist = .25, 
             z_method = "runif", z = 1, z_span = 3) %>%
  contour_shape(radius = 10.2, 
                x_center = 7, y_center = 7) 

# plot your data
contour_plot(setup$grid_shape) +
  ggplot2::xlim(1, 30) +
  ggplot2::ylim(1, 30)
```

## Example: with rings

```{r example-rings, fig.width=6, fig.height = 6}
#set up your data
setup = contour_grid(grid_size = 30, point_dist = .25, 
             z_method = "runif", z = 1, z_span = 3) %>%
  contour_shape(radius = 10.2, 
                x_center = 10, y_center = 10, 
                ring_system = "multiple",
                num_rings = 10)

# plot your data
contour_plot(setup$grid_shape, setup$rings) +
  ggplot2::xlim(1, 30) +
  ggplot2::ylim(1, 30)
```

## Example: without contour shape
```{r example-no-circle, fig.width=6, fig.height = 6}
#set up your data
setup = contour_grid(grid_size = 30, point_dist = .25, 
             z_method = "runif", z = 1, z_span = 3)

# plot your data
contour_plot(setup) +
  ggplot2::xlim(1, 30) +
  ggplot2::ylim(1, 30)
```
